%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Professional Services Delivery Engineer} % Job title
    {Rackspace Technology} % Organization
    {Amsterdam, The Netherlands} % Location
    {Feb 2022 - Oct 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and deployed cloud solutions using Terraform on Google Cloud.}
        \item {Developed an automated Kubernetes platform to streamline developer workflows.}
        \item {Mentored interns and other engineers.}
        \item {Containerized Ruby and Python web applications to enhance scalability and efficiency.}
        \item {Consulted teams on optimizing their software development lifecycle for improved efficiency.}
        \item {Identified and contributed solutions to security vulnerabilities in CI/CD pipelines, enhancing overall system security.}
      \end{cvitems}
    }
    {\textbf{Google Cloud}, \textbf{Terraform}, \textbf{Ansible}, \textbf{Podman}, \textbf{Linux}, \textbf{GitHub Actions}, \textbf{Kubernetes}, \textbf{Python}, \textbf{Ubuntu}, \textbf{RHEL}}
  \hl

%---------------------------------------------------------
  \cventry
    {Software/Automation Engineer} % Job title
    {Simbuka} % Organization
    {Best, The Netherlands} % Location
    {Feb 2017 - Jan 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a software development team from ideation to planning, and development to operations in an agile fashion.}
        \item {Developed loan origination software leveraging PHP and MySQL, ensuring robust functionality and scalability.}
        \item {Used observability and tracing tools to improve application performance.}
        \item {Utilized MindsDB to create predictive models from loan origination and arrears data.}
        \item {Application modernization by using devops and gitops methodologies.}
        \item {Containerized PHP web applications to enhance deployment efficiency and maximize scalability.}
        \item {Configured Proxmox servers with Ubuntu and Kubernetes for test and staging environments.}
        \item {Designed and implemented comprehensive end-to-end tests for web applications using Selenium to improve reliability and user experience.}
        \item {Crafted and maintained automation and CI/CD pipelines utilizing GitHub Actions to streamline development workflows.}
        \item {Performed system administration tasks on Red Hat Enterprise Linux, ensuring high system availability and performance.}
        \item {Managed and administered a MariaDB Galera database cluster, optimizing database operations for high availability and scalability.}
      \end{cvitems}
    }
    {\textbf{PHP}, \textbf{Laravel}, \textbf{MySQL}, \textbf{Kubernetes}, \textbf{Docker}, \textbf{Python}, \textbf{Grafana}, \textbf{InfluxDB}, \textbf{Linux}, \textbf{Ubuntu}, \textbf{RHEL}, \textbf{MySQL}, \textbf{Proxmox}, \textbf{GitHub Actions}, \textbf{MindsDB}}

\newpage

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {XSARUS} % Organization
    {Middelharnis, The Netherlands} % Location
    {Feb 2015 - Nov 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed scalable e-commerce solutions for multiple online retailers.}
        \item {Developed warehouse management systems for multiple retailers}
        \item {Connected online stores with major marketplaces for seamless sales and inventory sync.}
      \end{cvitems}
    }
    {\textbf{PHP}, \textbf{Zend Framework}, \textbf{MySQL}}
  \hl

%---------------------------------------------------------

  \cventry
  {Web Developer} % Job title
  {Freelancer} % Organization
  {The Netherlands} % Location
  {2012 - 2016} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed internal tools with Python and Django}
      \item {Developed webshops and website with WordPress and WooCommerce}
      \item {Developed webshops with OpenCart}
    \end{cvitems}
  }
  {\textbf{Javascript}, \textbf{Python}, \textbf{Django}, \textbf{PHP}, \textbf{MySQL}, \textbf{Wordpress}, \textbf{WooCommerce}}
  \hl

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {Bax Music} % Organization
    {Goes, The Netherlands} % Location
    {May 2014 - Jan 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the development of an in-house Returns Merchandise Authorization (RMA) system to streamline the returns process, reduce handling times, and improve customer satisfaction.}
        \item {Collaborated in cross-functional teams to deliver new features for the Magento-based e-commerce platform, enhancing both user and admin functionality.}
        \item {Integrated AngularJS into the system for building interactive and user-friendly interfaces.}
      \end{cvitems}
    }
    {\textbf{PHP}, \textbf{MySQL}, \textbf{Magento}, \textbf{AngularJS}, \textbf{ThreeJS}}
  \hl

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {Colijn IT} % Organization
    {Goes, The Netherlands} % Location
    {Jul 2013 - Apr 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented custom Magento themes to align with client-specific branding and functionality requirements, increasing customer appeal.}
        \item {Played a key role in deploying and maintaining multiple Magento webshops, ensuring seamless performance and high traffic handling.  }
        \item {Supported clients post-deployment, providing guidance on system usage and troubleshooting, leading to long-term client satisfaction and retention.}
        \item {Developed a prototype for an interactive 3D furniture design web application.}
      \end{cvitems}
    }
    {\textbf{PHP}, \textbf{MySQL}, \textbf{Magento}, \textbf{AngularJS}}
%---------------------------------------------------------

\end{cventries}

